Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-17 paper.tex
Edit involutive example

\paragraph{Lazy Insertion.}
Adding a hypothesis to a rule state is fairly cheap, but not free: it involves one unification for each premise that the hypothesis likely matches (according to a discrimination tree index), followed by several operations on the variable indices.
We therefore delay insertions until the index has selected at least one hypothesis for each slot.
This helps, for example, with the definitional rule for involutive functions: if $f : α → α$ is involutive, then for any $a : α$ we have $f (f a) = a$.
When used as a forward rule, the premise $a$ matches any non-propositional hypothesis, but this is only relevant if there is, in fact, an involutive function is the context.

>>>>

\paragraph{Lazy Insertion.}
Adding a hypothesis to a rule state is fairly cheap, but not free: it involves one unification for each premise that the hypothesis likely matches (according to a discrimination tree index), followed by several operations on the variable indices.
We therefore delay insertions until the index has selected at least one hypothesis for each slot.
This helps, for example, with the defining rule for involutive functions: if $f : α → α$ is involutive, then for any $a : α$ we have $f (f a) = a$.
When this rule is used as a forward rule, the premise $a$ matches any non-propositional hypothesis, but with lazy insertion we only process $a$ if there is, in fact, an involutive function is the context.
